Sample variance in weak lensing: how many simulations are required?

### 2016-01-08 Paper/paper.tex
implemented suggested edits

We measure the $\kappa$ angular power spectrum $P^{\kappa\kappa}_r(\ell)$ defined as
\begin{equation}
\langle\tilde{\kappa}_r(\pmb{\ell})\tilde{\kappa}_r(\pmb{\ell}')\rangle = (2\pi)^2\delta_D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}_r(\ell)
\end{equation}
%
As an additional summary statistic, we consider the counts of local
$\kappa$ maxima of a certain height $\kappa_0$, $n_r(\kappa_0)$
(hereafter \textit{peak counts}), with varying $\kappa_0$.
%ZH: state here the range and binning choice of $\kappa_0$
The fact that the ensemble of $N_r$ realizations is not completely
independent if $N_s$ is not large enough can have an effect on the
covariance estimators of both $P^{\kappa\kappa}$ and $n(\kappa_0)$.

@@

To measure the cosmological dependence of the $\kappa$ peak counts, we also performed additional ray--tracing simulations with different combinations of the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$ as outlined in Table \ref{simtable}.

\subsection{Cosmological parameter inference}
%

Let $\bbh{d}$ be a single estimate for a feature of dimension $N_b$, 
%ZH: ``Hat'' here refers to an estimator?
$\bb{d}(\bb{p})$ be the
%smooth expectation
%ZH: I believe ``smooth expectation'' means true mean value, yes?
true mean value of this feature at a point $\bb{p}$ in parameter space
(which has a dimension $N_p$) and $\bb{C}$ be the $N_b\times N_b$
feature covariance matrix. For the purpose of this work $\bb{p}$ is
the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is one of the
features -- either a power spectrum or a peak count -- in Table
\ref{featuretable}. While in many cases $\bb{d}(\bb{p})$ can be
predicted reasonably accurately by already existing emulators (see
\citep{coyote2,Nicaea} for example), the matter is more complicated
for covariance matrices.
%ZH: I am missing the point here.  Why is covariance matrix ``more complicated'' ?
%    Even to estimate a mean, one has to ``generate a series of mock realizations''.
%    Unless you are willing to equate a single realization as the mean.   But then
%    by the same logic, you could estimate the covariance matrix from two realizations.
%    Please clarify what you mean...  maybe I am missing something?  Or you simply mean
%    that published emulators usually do not emulate the cov.matrix (even though they could)?
%    Note that there is a paper by Schneider and Knox, in which they do an interpolation of the
%    power spectrum covariance matrix.
Estimating $\bb{C}$ from simulations involves generating a series of
mock realizations $\bbh{d}_r$ with $r=1...N_r$ and computing the
sample covariance $\bbh{C}$,

@@

\begin{table}
\begin{center}
\begin{tabular}{c|c|c||c|c|c}
\toprule
$\Omega_m$ &  $w$ & $\sigma_8$ & $N_s$ & $N_r$ & Number of $\kappa$ ensembles \\ \hline \hline
\midrule
%
0.26 & $-$1 & 0.8 & $1\div200$ & $1024\div128000$ & 16 \\
0.29 & $-$1 & 0.8 & 1 & 1024 & 1 \\
0.26 & $-$0.8 & 0.8 & 1 & 1024 & 1 \\
0.26 & $-$1 & 0.6 & 1 & 1024 & 1 \\
%
\bottomrule
\end{tabular}
\end{center}
\caption{Summary of the shear ensembles used in this work.}
%ZH: So each of these have N_r=1000, yes?  You should state this here. And also,
%    Add the ensemble with N_s=1, N_r=10^5 to this table.
%    Also: point the reader to this table in the text, up front, when the 
%    ensembles are first discussed.
\label{simtable}
\end{table}

@@

\begin{enumerate}
\item If the true data covariance $\bb{C}$ is known, the estimator in
  Eq.~(\ref{estimatorcovariance}) is biased, and the dominant
  contribution of the bias comes from the second order fluctuations in
  $\bbh{\Psi}$. Once the expectation values over simulations are
  taken, the bias sums up to

@@

\item Usually the true data covariance is unknown, and it is tempting
  to plug in its estimator $\bbh{C}$, measured from the same
  simulation set we use to compute $\bbh{\Psi}$. This approach has
  been used before in the literature
  (e.g.~\citep{MinkPetri,MinkShirasaki}). If this is done without
  correcting for the bias in $\bbh{\Psi}$ (see Eq.~\ref{firstmoment}
  below), 
%ZH: we should probably cite Hartlap et al. and Taylor et al. here for this Psi bias.  (I assume this is what you mean in eq. 19)
  the parameter variance will have a contribution from both the second
  and first-order fluctuations in $\bbh{\Psi}$, which now have a
  nonzero expectation value. In this case the bias sums up to
%
\begin{equation}
\label{mockscalinguncorrected}
\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1-\frac{N_b-N_p}{N_r}\right).
\end{equation}

@@

\end{enumerate} 
%
The error degradation in each parameter $p$, at leading order, scales
as $D/N_r$, where $D=N_b-N_p$, $N_p-N_b$, and $1+N_p$ for cases 1, 2,
and 3, respectively.
%ZH: It was not clear to me what the main point of the text below was. I paraphrased it slightly. OK?
%This means that, when parameter errors are
%estimated purely from simulations, and the same simulation set is used
%to estimate both $\bbh{C},\bbh{\Psi}$, these errors tend to decrease
%with $N_b$ (case 2), or at best remain constant (case 3), while the
%distribution of $\bbh{p}$ has still a variance that increases with
%$N_b$. This typically leads to underestimates in parameter errors. 
Note that in the last case, which is most relevant when fitting actual
data, the noise in both $\bbh{C}$ and $\bbh{\Psi}$ together degrade
the confidence limits.  However, this degradation turns out to be less
severe than in the idealized case 1 of a noiseless $\bbh{C}$ (assuming
$N_b\gg N_p$).  We also note that the distribution of $\bbh{p}$ has a
variance ($\Sigma_\bb{p}$) that increases with $N_b$, but the bias in
$\h{\Sigma}_\bb{p}$ is independent of $N_b$ in the realistic case 3.

We derived the scaling relations of the form
%
\begin{equation}
\label{ourscaling}
\langle\h{\sigma}_p^2\rangle = \sigma^2_{p,\infty}(N_s)\left(1+\frac{D}{N_r}\right)
\end{equation}
%
above by assuming that the noise in both $\bbh{C}$ and $\bbh{\Psi}$ is
Gaussian.  We next directly test these scaling relations using our
simulations, in the limits of both high and low $N_r$.
%ZH: It is still a little unclear here what is being tested.  Is it the Gaussianity assumption? I added that.
%    But perhaps you had some other issue in mind.
We use the notation $\h{\sigma}^2_p=\h{\Sigma}_{pp}$ 
%ZH: I am confused.  Why is a new symbol \sigma necessary here, on top of \Sigma ?
%    (And also: here you write \Sigma_pp, but above it was denoted \Sigma_p  )
and we indicate by $\sigma^2_{p,\infty}$ the expectation value of the
variance in the limit of an infinite number of realizations
$N_r\rightarrow\infty$.  We call $D$ the \textit{effective
  dimensionality} of the feature space (which, as seen before, can be
negative in some pathological cases).
%ZH: I added pathological here.  Do you agree?  It's only negative in case 1, when
%    N_p > N_b (which is impossible -- cannot measure N_p parameters with N_b observables)
%    or in case 2 (when N_b > N_p, so that's OK, but this case ust means we ``forgot'' to correct for the psi-bias).
We compute the expectation values of $\h{\sigma}^2_p$
(equations~\ref{estimatorcovariance} and \ref{ourscaling}) by
averaging over 100 random resamplings of our shear ensembles. For the
true feature covariance matrix
$\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use
the estimated covariance from a grand ensemble built with the union of
all the ensembles with different $N_s$.

@@

\begin{figure*}
\includegraphics[scale=0.4]{Figures/ps_pdf.eps}
\caption{PDF of the $\kappa$ power spectrum
  $\mathcal{L}(P_l^{\kappa\kappa})$ at four selected multipoles
  $\ell=115,344,1349,5283$, for different shear ensembles constructed
  from on $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), and 100
  (purple) independent N-body simulations. Each curve is based on
  $N_r=1000$ realizations.
%ZH: I added the Nr=1000 above. Yes?
  The thick
  black curves correspond to ensembles generated with $N_s=1$ and
  $N_r=10^5$. For $N_s\geq2$, the distributions appear
  similar to the eye; this similarity is confirmed by the comparisons
  in Figures \ref{means_ns} and \ref{ps_var} below. }
%added last two sentences. -Morgan
%Also: Thick black line draws the eye and looks like the most significant thing on the plot. replace with dotted black line or something else that stands out less.-Morgan
%ZH: Also, include a label ``N_r=10^5'' with the other N_s=... labels in the figure panels 
%   (it is just confusing why there are labels for all the other curves, but not for the thick black)
\label{ps_pdf}
\end{figure*}

\begin{figure}
\includegraphics[scale=0.3]{Figures/means_ns.eps}
\caption{The mean value 
 $\bb{\bar{d}}$
% $d$  
%ZH: I think you mean  \bb{\bar{d}} here?  You introduced a lot of different
%    subtle notations in the previous section, so we should  follow those ....
  of various features, measured from ensembles created from different
  numbers $N_s$ of simulations.  For each case, the difference compared
  to the mean in the $N_s=200$ ensemble is shown, in units of the
  statistical error measured in the $N_s=200$ ensemble.  The colored
  curves refer to shear-shear power spectra measured at $\ell=115$
  (black), 1027 (cyan), and 5283 (green), and peak counts 
%of
%ZH: I replace ``of'' with ``above''.  These are cumulative peak counts N(>kappa_0) ?
%    Or do you mean differential counts in some delta-kappa_0 bins?   Then you should
%    correct the text (and state the bin width).  Table II contains some kappa-bins
%    but no obvious relation to the 0.05, 0.17  and 0.28 mentioned here...
  with height above $\kappa_0=0.05$ (red), 0.17 (purple), and 0.28
  (orange).  For $N_s\geq 2$, the means are statistically
  indistinguishable from the means measured in the ensemble with $N_s=200$.}
%MM: added last sentence stating conclusion to be drawn from the figure
%ZH:  Good idea.  All figures captions should similarly state a conclusion!
%ZH:  What is the horizontal dashed line?  It is never mentioned in the caption or
%     the text.   I guess you decided to mark the ``0.1 sigma'' deviation?
%     We should state that.    I suppose this is what Morgan refers to by 
%    ``statistically indistinguishable'' ....  0.1 sigma.
\label{means_ns}
\end{figure}

\begin{figure}
\includegraphics[scale=0.3]{Figures/ps_variance.eps}
\caption{Variance of the $\kappa$ power spectrum as a function of the
  multipole $\ell$, in units of the expected Gaussian variance from
  equation (\ref{gaussianvar}). The variance is measured from
  different shear ensembles based on $N_s=$1 (black), 2 (blue), 5
  (green), 10 (red), 50 (purple), or 100 (orange) N-body simulations. 
%ZH: Added ``conclusion'':
  Non-Gaussianities of the underlying structures increase the variance on
  small scales, but no clear trend with $N_s$ can be identied on any scale.}
\label{ps_var}
\end{figure}

\begin{figure}
\includegraphics[scale=0.3]{Figures/curving_nb.eps}
\caption{Expectation value of the variance of $w$ computed from
  equation (\ref{estimatorcovariance}), shown as a function of
  $1/N_r$. The different symbols and colors correspond to the features
  listed in Table~\ref{featuretable}.
%ZH: It would be better to write the features on the legend embedded in the figure.
%    Why make the reader flip back-and-forth between the figure and the Table ?
  The dashed and solid curves show the analytic predictions from
  equation (\ref{quarticdegradation}) at orders $O(1/N_r)$ and
  $O(1/N_r^2)$, respectively. The asymptotic variance
  $\sigma^2_{w,\infty}$ has been computed from a linear regression of
  $\langle\h{\sigma}^2_w\rangle$ vs $1/N_r$ for $N_r>500$. The figure
  clearly shows that terms beyond $O(1/N_r)$ need to be considered,
  unless $N_r\gg N_b$.}
%MM: added last sentence stating conclusion to be drawn from the figure
%in legend box change line that reads Nb=7 divided by 8
\label{curvingnb}
\end{figure}

\begin{figure}
\includegraphics[scale=0.3]{Figures/scaling_nr.eps}
\caption{Bias in the variance of $w$,
  $\langle\h{\sigma}^2_w\rangle-\sigma^2_{w,\infty}$, as a function of
  the number of realizations $N_r$ used to estimate the covariance
  (eq.~\ref{covest}). Results for different ensembles, generated from
  $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), and 100 (purple)
  simulations are shown. The figure shows both the measured trends
  (solid lines) and their best fits based on eq.~(\ref{ourscaling}),
  with $D$ treated as a free parameter.
%ZH: We need to explain what you mean by best-fit (presumably you treat ``D'' as a free parameter).
%   I added that. But if you meant something else, please correct.
  The thick black curve corresponds to an ensemble of $N_r=10^5$
  realizations from a single simulation ($N_s=1$).
%ZH: I added 'conclusion':
  No systematic deviation from the expected scaling is seen, even in
  the extreme last case.  }
\label{wvar_nr}
\end{figure}

\begin{figure}
\includegraphics[scale=0.3]{Figures/scaling_ns.eps}
\caption{The variance of $w$ in the limit of $N_r\rightarrow\infty$,
%ZH: state here what N_r was actually used to approximate the infinity limit
  varying the number of simulations $N_s$ used in the ensemble to
  estimate the covariance (eq.~\ref{covest}). We show the dependence
  of $\sigma_{w,\infty}^2(N_s)$ in units of the mean over $N_s$, 
%ZH: Just to make sure: what you mean here is an averaging of sigma_infty over the 16 different
%    cases of N_s ?   
  for
  the power spectrum logarithmically binned (black), the power
  spectrum linearly binned (red) and the peak counts (green).
%ZH: What ell and kappa ranges were used?
%ZH: Added conclusion:
  No trend with $N_s$ is seen for $N_s\geq 2$, and the
  differences are only 1\%.  }
\label{wvar_ns}
\end{figure}

@@

In this section we present the main results of this work. We show the
qualitative behavior of a variety of feature $\bbh{d}_r$ probability
distribution functions (PDFs) in ensembles built with different $N_s$
and $N_r$. In Figure~\ref{ps_pdf}, we show the PDF of the power
spectrum at four selected multipoles, spanning the linear ($\ell=115$)
to the nonlinear ($\ell=5283$) regime. In Figure~\ref{means_ns}, we
shows the ensemble mean for these power spectra, as well as for peak
counts above three different $\kappa$ thresholds (corresponding to
$\approx 2-12\sigma$ peaks), as a function of $N_s$.
%ZH: added above 2-12.  OK ?
In Figure~\ref{ps_var}, we show the variance of the power spectrum at
each multipole, as a function of $N_s$, in units of the variance
expected if the convergence $\kappa$ was a Gaussian random field
%
%ZH:  I changed ``l''  to ``\ell'' in many places, for the multipole
\begin{equation}
\label{gaussianvar}
\mathrm{Var}(P^{\kappa\kappa}_\ell) = \frac{(P^{\kappa\kappa}_\ell)^2}{N_{\rm eff}(\ell).}
\end{equation}
%
Here $N_{\rm eff}(l)$ is the number of independent modes used to
estimate the power spectrum at $\ell$.

In practice, we measure $P^{\kappa\kappa}_\ell$ on the Fourier
transform of the pixelized simulated map $\kappa_r(\pmb{\theta})$,
using the FFT algorithm, and some care must be taken to count the
number of modes $N_{\rm eff}(\ell)$ correctly. Each pixel $(i_x,j_y)$
in Fourier space corresponds to a mode
$(\ell_x,\ell_y)=2\pi(i_x,i_y)/\theta_{\rm box}$, with $i_x=-n_{\rm
  ray}/2,...,n_{\rm ray}/2$ and $i_y=0,...,n_{\rm ray}/2$.
%ZH: added this:
Here $n_{\rm ray}=2048$ is the linear number of pixels on the
ray-traced convergence maps.  We count the number of pixels $N(\ell)$
that fall inside a multipole bin $(\ell_1,\ell_2)$. Because the
$\kappa$ field is real, the modes $(\pm \ell_x,0)$ are not
independent. If we let $N(\ell,\ell_y=0)$ be the number of
non--independent modes, the effective number of independent modes
for the variance is given by

>>>>

We measure the $\kappa$ angular power spectrum $P^{\kappa\kappa}_r(\ell)$ defined as
\begin{equation}
\langle\tilde{\kappa}_r(\pmb{\ell})\tilde{\kappa}_r(\pmb{\ell}')\rangle = (2\pi)^2\delta_D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}_r(\ell)
\end{equation}
%
As an additional summary statistic, we consider the counts of local
$\kappa$ maxima of a certain height $\kappa_0$, $n_r(\kappa_0)$
(hereafter \textit{peak counts}), with varying $\kappa_0$ chosen between the minimum and maximum values measured from the maps $(\kappa_{\rm min},\kappa_{\rm max})=(-0.06,0.45)$. Different choices of $\kappa_0$ binning used in this work are outlined in Table \ref{featuretable}. 
%ZH: state here the range and binning choice of $\kappa_0$
%AP: done
The fact that the ensemble of $N_r$ realizations is not completely
independent if $N_s$ is not large enough can have an effect on the
covariance estimators of both $P^{\kappa\kappa}$ and $n(\kappa_0)$.

@@

To measure the cosmological dependence of the $\kappa$ peak counts, we also performed additional ray--tracing simulations with different combinations of the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$. A summary of the complete set of shear ensembles used in this work is outlined in Table \ref{simtable}.

\subsection{Cosmological parameter inference}
%
Let $\bbh{d}$ be a single estimate for a feature of dimension $N_b$, 
%ZH: ``Hat'' here refers to an estimator?
%AP: Yes: quantities without the hat are the expectation values 
$\bb{d}(\bb{p})$ be the
%smooth expectation
%ZH: I believe ``smooth expectation'' means true mean value, yes?
%AP: yes
true value of this feature at a point $\bb{p}$ in parameter space
(which has a dimension $N_p$) and $\bb{C}$ be the $N_b\times N_b$
feature covariance matrix. For the purpose of this work $\bb{p}$ is
the triplet $(\Omega_m,w,\sigma_8)$ and $\bb{d}$ is one of the
features -- either a power spectrum or a peak count histogram -- in Table
\ref{featuretable}. Although existing emulators (see
\citep{coyote2,Nicaea,SchneiderKnoxCovariance} for example) can be used to compute $\bb{d}(\bb{p}),\bb{C}$ in some cases, this is not true in the general case. 
%ZH: I am missing the point here.  Why is covariance matrix ``more complicated'' ?
%    Even to estimate a mean, one has to ``generate a series of mock realizations''.
%    Unless you are willing to equate a single realization as the mean.   But then
%    by the same logic, you could estimate the covariance matrix from two realizations.
%    Please clarify what you mean...  maybe I am missing something?  Or you simply mean
%    that published emulators usually do not emulate the cov.matrix (even though they could)?
%    Note that there is a paper by Schneider and Knox, in which they do an interpolation of the
%    power spectrum covariance matrix.
%AP: The intended meaning is the latter: published emulators only predict the means. It is also true that getting the covariance accurate is more difficult than getting the means accurate. I rephrased the sentence.
Estimating $\bb{C}$ from simulations involves generating a series of mock realizations $\bbh{d}_r$ with $r=1...N_r$ and computing the
sample covariance $\bbh{C}$,

@@

\begin{table*}
\begin{center}
\begin{tabular}{c|c|c||c|c}
\toprule
$\Omega_m$ &  $w$ & $\sigma_8$ & $(N_s,N_r)$ & Number of $\kappa$ ensembles \\ \hline \hline
\midrule
%
0.26 & $-$1 & 0.8 & $(1\div200,1024),(1,128000)$ & 16 \\
0.29 & $-$1 & 0.8 & (1,1024) & 1 \\
0.26 & $-$0.8 & 0.8 & (1,1024) & 1 \\
0.26 & $-$1 & 0.6 & (1,1024) & 1 \\
%
\bottomrule
\end{tabular}
\end{center}
\caption{Summary of the shear ensembles used in this work.}
%ZH: So each of these have N_r=1000, yes?  You should state this here. And also,
%    Add the ensemble with N_s=1, N_r=10^5 to this table.
%    Also: point the reader to this table in the text, up front, when the 
%    ensembles are first discussed.
%AP: done
\label{simtable}
\end{table*}

@@

\begin{enumerate}
\item If the true data covariance $\bb{C}$ is known, the estimator in eq.~(\ref{estimatorcovariance}) is biased, and the dominant contribution of the bias comes from the second order fluctuations in $\bbh{\Psi}$. Once the expectation values over simulations are taken, the bias sums up to

@@

\item Usually the true data covariance is unknown, and it is tempting to plug in its estimator $\bbh{C}$, measured from the same simulation set we use to compute $\bbh{\Psi}$. This approach has been used before in the literature (e.g.~\citep{MinkPetri,MinkShirasaki}). If this is done without correcting for the bias in $\bbh{\Psi}$ (see eq.~(\ref{firstmoment}) below or \citep{Taylor12} for reference), 
%ZH: we should probably cite Hartlap et al. and Taylor et al. here for this Psi bias.  (I assume this is what you mean in eq. 19)
%AP: done
the parameter variance will have a contribution from both the second and first-order fluctuations in $\bbh{\Psi}$, which now have a nonzero expectation value. In this case the bias sums up to
%
\begin{equation}
\label{mockscalinguncorrected}
\langle\h{\Sigma}_\bb{p}\rangle=\Sigma_\bb{p}\left(1-\frac{N_b-N_p}{N_r}\right).
\end{equation}

@@

\end{enumerate} 
%
The error degradation in each parameter $p$, at leading order, scales
as $D/N_r$, where $D=N_b-N_p$, $N_p-N_b$, and $1+N_p$ for cases 1, 2,
and 3, respectively.
%ZH: It was not clear to me what the main point of the text below was. I paraphrased it slightly. OK?
%This means that, when parameter errors are
%estimated purely from simulations, and the same simulation set is used
%to estimate both $\bbh{C},\bbh{\Psi}$, these errors tend to decrease
%with $N_b$ (case 2), or at best remain constant (case 3), while the
%distribution of $\bbh{p}$ has still a variance that increases with
%$N_b$. This typically leads to underestimates in parameter errors. 
%AP: Not exactly: my point was that the distribution of \bbh{p} has a true variance that increases with Nb, but the estimate of this variance (which we quote as the errorbar) does not increase with Nb. Hence we get the wrong parameter fit (i.e. which excludes the true value at high significance level)
Note that in the last case, which is most relevant when fitting actual data, the estimated degradation turns out to be too optimistic: the parameter estimate $\bbh{p}$ has a variance that grows linearly with $N_b$, but the estimated degradation in eq. (\ref{mockscalingcorrected}) is constant with $N_b$. This can lead to underestimation of error bars, which can be mistakenly interpreted as a parameter bias.  
We derived the scaling relations of the form
%
\begin{equation}
\label{ourscaling}
\langle\h{\sigma}_p^2\rangle = \sigma^2_{p,\infty}(N_s)\left(1+\frac{D}{N_r}\right)
\end{equation}
%
above by assuming that the noise in $\bbh{d}$ is Gaussian. We then directly test these scaling relations using our simulations, in the limits of both high and low $N_r$.
%ZH: It is still a little unclear here what is being tested.  Is it the Gaussianity assumption? I added that.
%    But perhaps you had some other issue in mind.
%AP: The noise in $\bbh{C}$ and $\bbh{\Psi}$ is not Gaussian: if the data vector from which $\bbh{C}$ and $\bbh{\Psi}$ are estimated in Gaussian, then these matrices are distibuted according to, respectively, the Wishart and inverse Wishart distributions. We are testing that the degradation effectively decreases as 1/Nr at leading order.  
We indicate the diagonal elements of $\h{\Sigma}_{\bb{p}}$ as $\h{\sigma}^2_p=\mathrm{diag}(\h{\Sigma}_{\bb{p}})$ 
%ZH: I am confused.  Why is a new symbol \sigma necessary here, on top of \Sigma ?
%    (And also: here you write \Sigma_pp, but above it was denoted \Sigma_p  )
%AP: fixed. I introduced the \sigma symbol for the single parameter variances (as opposed to the full parameter covariance), because these are the quantities we plot
and we indicate by $\sigma^2_{p,\infty}$ the expectation value of the variance of each parameter in the limit of an infinite number of realizations
$N_r\rightarrow\infty$.  We call $D$ the \textit{effective dimensionality} of the feature space (which, as seen before, can be
negative in some pathological cases).
%ZH: I added pathological here.  Do you agree?  It's only negative in case 1, when
%    N_p > N_b (which is impossible -- cannot measure N_p parameters with N_b observables)
%    or in case 2 (when N_b > N_p, so that's OK, but this case ust means we ``forgot'' to correct for the psi-bias).
%AP: agreed
We compute the expectation values of $\h{\sigma}^2_p$
(eqs.~\ref{estimatorcovariance} and \ref{ourscaling}) by
averaging over 100 random resamplings of our shear ensembles. For the
true feature covariance matrix $\langle(\bbh{d}-\bb{d}_0)(\bbh{d}-\bb{d}_0)^T\rangle=\bb{C}$ we use
the estimated covariance from a grand ensemble built with the union of
all the ensembles with different $N_s$.

@@

\begin{figure*}
\includegraphics[scale=0.4]{Figures/ps_pdf.eps}
\caption{PDF of the $\kappa$ power spectrum
  $\mathcal{L}(P_l^{\kappa\kappa})$ at four selected multipoles
  $\ell=115,344,1349,5283$, for different shear ensembles constructed
  from on $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), and 100
  (purple) independent N-body simulations. Each curve is based on
  $N_r=1024$ realizations.
%ZH: I added the Nr=1000 above. Yes?
%AP: Yes, 1024 in reality, but it doesn't change much
  The dashed black curves correspond to ensembles generated with $N_s=1$ and
  $N_r=128000$. For $N_s\geq2$, the distributions appear
  similar to the eye; this similarity is confirmed by the comparisons
  in Figures \ref{means_ns} and \ref{ps_var} below.}
%MM: added last two sentences
%MM: Thick black line draws the eye and looks like the most significant thing on the plot. replace with dotted black line or something else that stands out less.
%ZH: Also, include a label ``N_r=10^5'' with the other N_s=... labels in the figure panels 
%   (it is just confusing why there are labels for all the other curves, but not for the thick black)
%AP: done
\label{ps_pdf}
\end{figure*}

\begin{figure}
\includegraphics[scale=0.3]{Figures/means_ns.eps}
\caption{The mean value $\bb{\bar{d}}$
% $d$  
%ZH: I think you mean  \bb{\bar{d}} here?  You introduced a lot of different
%    subtle notations in the previous section, so we should  follow those ....
%AP: OK
  of various features, measured from ensembles created from different
  numbers $N_s$ of simulations.  For each case, the difference compared
  to the mean in the $N_s=200$ ensemble is shown, in units of the
  statistical error measured in the $N_s=200$ ensemble.  The colored
  curves refer to shear--shear power spectra measured at $\ell=115$
  (black), 1027 (cyan), and 5283 (green), and peak counts 
%ZH: I replace ``of'' with ``above''.  These are cumulative peak counts N(>kappa_0) ?
%    Or do you mean differential counts in some delta-kappa_0 bins?   Then you should
%    correct the text (and state the bin width).  Table II contains some kappa-bins
%    but no obvious relation to the 0.05, 0.17  and 0.28 mentioned here...
%AP: The peak counts are differential, I added the clarifications; I chose three values of kappa0 for the sake of presentation simplicity (one value in the low height peaks, one in the middle and one in the large)
  with height of $\kappa_0=0.05$ (red), 0.17 (purple), and 0.28
  (orange). The $\kappa$ bin width for the peak counts has been fixed to $\Delta\kappa=0.011$. The dashed black line shows a level of $0.1\sigma$ accuracy for reference.  For $N_s\geq 2$, the means are statistically indistinguishable (at $\sim0.1\sigma$) from the means measured in the ensemble with $N_s=200$.}
%MM: added last sentence stating conclusion to be drawn from the figure
%ZH:  Good idea.  All figures captions should similarly state a conclusion!
%ZH:  What is the horizontal dashed line?  It is never mentioned in the caption or
%     the text.   I guess you decided to mark the ``0.1 sigma'' deviation?
%     We should state that.    I suppose this is what Morgan refers to by 
%    ``statistically indistinguishable'' ....  0.1 sigma.
%AP: Ok, added the clarifications to the caption
\label{means_ns}
\end{figure}

\begin{figure}
\includegraphics[scale=0.3]{Figures/ps_variance.eps}
\caption{Variance of the $\kappa$ power spectrum as a function of the
  multipole $\ell$, in units of the expected Gaussian variance from
  equation (\ref{gaussianvar}). The variance is measured from
  different shear ensembles based on $N_s=$1 (black), 2 (blue), 5
  (green), 10 (red), 50 (purple), or 100 (orange) N--body simulations. 
%ZH: Added ``conclusion'':
%AP: OK
  Non--Gaussianities of the underlying structures increase the variance on
  small scales, but no clear trend with $N_s$ can be identied on any scale.}
\label{ps_var}
\end{figure}

\begin{figure}
\includegraphics[scale=0.3]{Figures/curving_nb.eps}
\caption{Expectation value of the variance of $w$ computed from
  equation (\ref{estimatorcovariance}), shown as a function of
  $1/N_r$. The different symbols and colors correspond to the features
  listed in Table~\ref{featuretable}.
%ZH: It would be better to write the features on the legend embedded in the figure.
%    Why make the reader flip back-and-forth between the figure and the Table ?
%AP: done
  The dashed and solid curves show the analytic predictions from
  equation (\ref{quarticdegradation}) at orders $O(1/N_r)$ and
  $O(1/N_r^2)$, respectively. The asymptotic variance
  $\sigma^2_{w,\infty}$ has been computed from a linear regression of
  $\langle\h{\sigma}^2_w\rangle$ vs $1/N_r$ for $N_r>500$. The figure
  clearly shows that terms beyond $O(1/N_r)$ need to be considered,
  unless $N_r\gg N_b$.}
%MM: added last sentence stating conclusion to be drawn from the figure
%in legend box change line that reads Nb=7 divided by 8
%AP: done, the legend is comprehensive now
\label{curvingnb}
\end{figure}

\begin{figure}
\includegraphics[scale=0.3]{Figures/scaling_nr.eps}
\caption{Bias in the variance of $w$,
  $\langle\h{\sigma}^2_w\rangle-\sigma^2_{w,\infty}$, as a function of
  the number of realizations $N_r$ used to estimate the covariance
  (eq.~\ref{covest}). Results for different ensembles, generated from
  $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), and 100 (purple)
  simulations are shown. The figure shows both the measured trends
  (solid lines) and their best fits based on eq.~(\ref{ourscaling}),
  with $D$ treated as a free parameter.
%ZH: We need to explain what you mean by best-fit (presumably you treat ``D'' as a free parameter).
%   I added that. But if you meant something else, please correct.
%AP: OK
  The thick black curve corresponds to an ensemble of $N_r=128000$
  realizations from a single simulation ($N_s=1$).
%ZH: I added 'conclusion':
%AP: OK
  No systematic deviation from the expected scaling is seen, even in
  the extreme last case.  }
\label{wvar_nr}
\end{figure}

\begin{figure}
\includegraphics[scale=0.3]{Figures/scaling_ns.eps}
\caption{The variance of $w$ in the limit of $N_r\rightarrow\infty$ (measured from the intercept of the fit $\sigma^2_w$ vs $1/N_r$),
%ZH: state here what N_r was actually used to approximate the infinity limit
%AP: the value plotted is actually $N_r\rightarrow\infty$, because it is estimated from the intercept of the fit. Even if all the points have Nr finite, the intercept of the line corresponds to Nr infinite. 
  varying the number of simulations $N_s$ used in the ensemble to
  estimate the covariance (eq.~\ref{covest}). We show the dependence
  of $\sigma_{w,\infty}^2(N_s)$ in units of the mean over the 16 ensembles with different $N_s$, 
%ZH: Just to make sure: what you mean here is an averaging of sigma_infty over the 16 different
%    cases of N_s ?   
%AP: Yes
  for the power spectrum logarithmically binned (black, $N_b=15,\ell\in[100,6000]$), the power spectrum linearly binned (red,$N_b=39,\ell\in[100,6000]$) and the peak counts (green,$N_b=45,\kappa_0\in[-0.06,0.45]$).
%ZH: What ell and kappa ranges were used?
%ZH: Added conclusion:
%AP: OK, added binning information
  No trend with $N_s$ is seen for $N_s\geq 2$, and the differences are only of order 1\%.}
\label{wvar_ns}
\end{figure}

@@

In this section we present the main results of this work. We show the
qualitative behavior of a variety of feature $\bbh{d}_r$ probability
distribution functions (PDFs) in ensembles built with different $N_s$
and $N_r$. In Figure~\ref{ps_pdf}, we show the PDF of the power
spectrum at four selected multipoles, spanning the linear ($\ell=115$)
to the nonlinear ($\ell=5283$) regime. In Figure~\ref{means_ns}, we
shows the ensemble mean for these power spectra, as well as for peak
counts of three different $\kappa_0$ heights (corresponding to
$\approx 2\div13\sigma$ peaks), as a function of $N_s$.
%ZH: added above 2-12.  OK ?
%AP: the actual numbers are 2-13, but again, only minor change
In Figure~\ref{ps_var}, we show the variance of the power spectrum at
each multipole, as a function of $N_s$, in units of the variance
expected if the convergence $\kappa$ was a Gaussian random field
%
%ZH:  I changed ``l''  to ``\ell'' in many places, for the multipole
%AP: OK, I fixed this throughout the rest of the paper
\begin{equation}
\label{gaussianvar}
\mathrm{Var}(P^{\kappa\kappa}_\ell) = \frac{(P^{\kappa\kappa}_\ell)^2}{N_{\rm eff}(\ell).}
\end{equation}
%
Here $N_{\rm eff}(l)$ is the number of independent modes used to
estimate the power spectrum at $\ell$.

In practice, we measure $P^{\kappa\kappa}_\ell$ on the Fourier
transform of the pixelized simulated map $\kappa_r(\pmb{\theta})$,
using the FFT algorithm, and some care must be taken to count the
number of modes $N_{\rm eff}(\ell)$ correctly. Each pixel $(i_x,j_y)$
in Fourier space corresponds to a mode
$(\ell_x,\ell_y)=2\pi(i_x,i_y)/\theta_{\rm box}$, with $i_x=-n_{\rm
  ray}/2,...,n_{\rm ray}/2$ and $i_y=0,...,n_{\rm ray}/2$.
%ZH: added this:
%AP: OK
Here $n_{\rm ray}=2048$ is the linear number of pixels on the
ray--traced convergence maps.  We count the number of pixels $N(\ell)$
that fall inside a multipole bin $(\ell_1,\ell_2)$. Because the
$\kappa$ field is real, the modes $(\pm \ell_x,0)$ are not
independent. If we let $N(\ell,\ell_y=0)$ be the number of
non--independent modes, the effective number of independent modes
for the variance is given by
